Title Goes Here

### 2020-02-15 paper/paper.tex
Possibly slightly less confusing naming
ConstructAp
Cabal

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Domain specific languages (DSLs) provide a powerful tool for to abstract over
  a class of problems. In this paper, we introduce a technique for representing
  algebraic data types and pattern matching in a DSL embedded in Haskell. This
  representation is automated through the use of GHC Generics and Template Haskell.
\end{abstract}

@@

\begin{lstlisting}
construct ::
  Construct (a -> b)
    => (a -> b) -> LiftedFn (a -> b)
construct = construct' . Construct

@@

The "helper constructor" \ttt{Construct} is part of the \ttt{E} type:

\begin{lstlisting}
data E t where
  ...
  Construct :: (a -> b) -> E (a -> b)
  ...
\end{lstlisting}

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Domain specific languages (DSLs) provide a powerful tool for to abstract over
  a class of problems. In this paper, we introduce a technique for representing
  algebraic data types and pattern matching in a DSL embedded in Haskell. This
  representation is mechanized through the use of GHC Generics and Template Haskell.
\end{abstract}

@@

\begin{lstlisting}
construct ::
  Construct (a -> b)
    => (a -> b) -> LiftedFn (a -> b)
construct = construct' . ConstructE

@@

The "helper constructors" \ttt{ConstructE} are part of the \ttt{E} type:

\begin{lstlisting}
data E t where
  ...
  ConstructE :: (a -> b) -> E (a -> b)
  ConstructAp :: ERep a => E (a -> b) -> E a -> E b
  ...
\end{lstlisting}
